Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2014-03-26 parts/sa.tex
debut sequencial reachability

\section{Static Analysis}\label{sec:sa}

@@

The semantics of PH with $2$ classes of priorities studied in this paper allows to model cooperative sorts accurately representing a coherent configuration of a set of sorts.
Therefore, we can derive a new method to conclude about the reachability of a state (considering only components).
Indeed, let $\PH = (\PHs, \PHl, (\PHh^{(1)}, \PHh^{(2)}))$ be a PH and suppose that we want to study the reachability of a state $s \in \PHl$.
Let $\PH' = (\PHs', \PHl', (\PHh'^{(1)}, \PHh'^{(2)}))$
with: $\PHs' = \PHs \cup \{ \total, \reach \}$ and $\PHl' = \PHl \times \PHl_\total \times \PHl_\reach$,
where $\total$ is a cooperative sort on all components $\components$ of $\PH$ (thus $\PHl_\total = \underset{a \in \components}{\times} \PHl_a$)
and $\reach$ is a component with $\PHl_\reach = \{ \reach_0, \reach_1 \}$;
furthermore, $\PHh'^{(1)}$ is the set $\PHh^{(1)}$ completed with all actions updating the cooperative sort $\total$,
and $\PHh'^{(2)} = \PHh^{(2)} \cup \{ \PHhit{\pfp_s(\total)}{\reach_0}{\reach_1} \}$.

@@

\todo{Loic? Maxime?}

>>>>

% vi:spell spelllang=en:
\section{Static Analysis}\label{sec:sa}

@@

The reachability property studied so far concern a single process, \ie{} the
local state of a single component.
However, we remark that the reachability of a partial or global state can be
addressed with the very same analysis by introducing a dedicated cooperative
sort in the scope of the PH semantics with $2$ classes of priorities.

Indeed, let $\PH = (\PHs, \PHl, (\PHh^{(1)}, \PHh^{(2)}))$ be a PH and suppose that we want to study the reachability of a state $s \in \PHl$.
Let $\PH' = (\PHs', \PHl', (\PHh'^{(1)}, \PHh'^{(2)}))$
with: $\PHs' = \PHs \cup \{ \total, \reach \}$ and $\PHl' = \PHl \times \PHl_\total \times \PHl_\reach$,
where $\total$ is a cooperative sort on all components $\components$ of $\PH$ (thus $\PHl_\total = \underset{a \in \components}{\times} \PHl_a$)
and $\reach$ is a component with $\PHl_\reach = \{ \reach_0, \reach_1 \}$;
furthermore, $\PHh'^{(1)}$ is the set $\PHh^{(1)}$ completed with all actions updating the cooperative sort $\total$,
and $\PHh'^{(2)} = \PHh^{(2)} \cup \{ \PHhit{\pfp_s(\total)}{\reach_0}{\reach_1} \}$.

@@

The sufficient condition for the reachability of a process from a given context
can be extended for the successive reachability of several processes ($a_i$,
then $b_j$, etc.) in the following manner.

\todo{}

\begin{definition}
\label{def:lastprocs}
\end{definition}

\begin{theorem}[Sequential under-approximation]
\label{thm:ordered-ua}
Given a context $\ctx$ and an objective sequence $\w =
P\concat\w'\in\OS$,
$\uconcr(P)\neq\emptyset \wedge
	\muconcr_{\ctx'}(\w')\neq\emptyset
	\Longrightarrow \uconcr(\w)\neq\emptyset$,
where $\ctx' = \procs(\mycwB{\ctx}{P})\Cap\lastprocs(P)$
\end{theorem}
